\subsection{Notation}
Define 
\begin{align}
    \ket{0} = \begin{pmatrix}
        1 \\
        0
    \end{pmatrix}, \ket{1} = \begin{pmatrix}
        0 \\ 
        1
    \end{pmatrix}
\end{align}

\begin{align}
    \ket{ij} = \ket{i} \otimes \ket{j}
\end{align}

\begin{align}
    X = \begin{pmatrix}
        0 & 1 \\
        1 & 0
    \end{pmatrix}, Y = \begin{pmatrix}
        0 & -i \\
        i & 0
    \end{pmatrix}, Z = \begin{pmatrix}
        1 & 0 \\
        0 & -1
    \end{pmatrix}
\end{align}

\subsection{Hamiltonians}
\subsubsection{$H \in \mathbb{R}^2$ Hamiltonian}
As an initial test, we will consider a simply $2\times 2$ real Hamiltonian consistend of a diagonal part $H_0$ and off-diagonal part $H_I$, playing the roles of a non-interactive one-body and interactive two-body part respectively. Defined through their matrix elements, we express them in the Pauli basis $\set{\ket{0},\ket{1}}$

\begin{align}
    \begin{split} \label[eq]{eq:theo:2times2_hamiltonian}
        H &= H_0 + H_I \\
        H_0 = \begin{pmatrix}
            E_1 & 0 \\
            0 & E_2
        \end{pmatrix}&, \hspace{20px}
        H_I = \lambda \begin{pmatrix}
            V_{11} & V_{12} \\
            V_{21} & V_{22}
        \end{pmatrix}
    \end{split}
\end{align}
Where $\lambda \in [0,1]$ is a coupling constant parameterizing the strength of the interaction. 

\subsubsection{$H \in \mathbb{R}^4$ Hamiltonian}
We now move on to a slightly larger system, defined as a $4 \times 4$ real Hamiltonian. This can be viewed as two  composite systems where each system is a two-level system. In the product basis $\set{\ket{00},\ket{01},\ket{10},\ket{11}}$ we define the one-body part as 
\begin{align}
    H_0 \ket{ij} = \epsilon_{ij}\ket{ij}, \label[eq]{eq:theo:4times4_diagonal_hamiltonian}
\end{align}
with a two-body interaction defined using Pauli matricies
\begin{align}
    \begin{split} \label[eq]{eq:theo:4times4_interaction}
        H_I &= H_x X \otimes X + H_z Z \otimes Z \\
        &= \begin{pmatrix}
            H_z & 0 & 0 & H_z \\
            0 & - H_z & H_x & 0 \\
            0 & H_x & - H_z & 0 \\
            H_x & 0 & 0 & H_z
        \end{pmatrix}
    \end{split}
\end{align}
Where $H_x$ and $H_y$ are couplings playing the same role as $\lambda$.

\subsubsection{Lipkin Model}
For larger many-body systems, the introduction of the occupation representation is common. The creation of a state $p$ is represented by the operator $\crt{p}$, while annihilation $\ani{p}$. Since we are dealing with fermions, the creation and annihilation operators follow the canonical anitcommutation relations
\begin{align}
    \set{\crt{p},\crt{q}} = \set{\ani{p},\ani{q}} = 0, \hspace{10px}\set{\crt{p},\ani{q}} = \delta_{pq}. 
    \label[eq]{eq:theo:car_algebra}
\end{align}
The Lipkin model \citep{lipkinValidityManybodyApproximation1965} for a $N$ fermion system consists of two energy levels $\sigma \in \set{\pm 1}$, each having a degeneracy of $N$. Resembling fermionic half integer spin, the two levels contributes energetically $\pm \frac{1}{2}\epsilon$ for each particle. Additionally, we label the different states in each degenerate level by $p = 1, \ldots N$ \footnote{This removes the spin quantum number from $p$, which commonly is included.}. The Lipkin Hamiltonian can be written using creation and annihilation operators as 
\begin{align}
    \begin{split}\label[eq]{eq:theo:lipkin_second_quant_hamiltonian}
    H &= H_0 + H_1 + H_2, \\
    H_0 &= \frac{1}{2}\epsilon \sum_{pq} \sigma \crt{p\sigma} \ani{p\sigma}, \\
    H_1 &= \frac{1}{2}V \sum_{pp'\sigma} \crt{p\sigma}\crt{p'\sigma}\ani{p'\bar{\sigma}}\ani{p\bar{\sigma}}, \\
    H_2 &= \frac{1}{2}W \sum_{pp'\sigma} \crt{p\sigma} \crt{p'\bar{\sigma}} \ani{p'\sigma} \ani{p\bar{\sigma}}.
    \end{split}
\end{align}
With $\bar{\sigma} = -\sigma$. $H_0$ is a diagonal single particle operator giving a contribution based on occupancy in the different levels. $H_1$ and $H_2$ are two-body operators moving pairs of particles between levels and exchanging particles between levels (spin-exchange) respectively. The strengths of these effects are parameterized by the couplings $V$ and $W$. By defining the \textit{quasi-spin} operators $J_\pm , J_z, J^2$ in addition to the number operator $N$ as 
\begin{align}
    \begin{split}\label[eq]{eq:theo:quasi_spin_definitions}
        J_\pm = \sum_p \crt{p\pm}\ani{p\mp} \\
        J_z = \frac{1}{2}\sum_{p\sigma} \sigma \crt{p\sigma} \ani{p\sigma} \\
        J^2 = J_+ J_- + J_z^2 - J_z \\
        N = \sum_{p\sigma} \crt{p\sigma} \ani{p\sigma}
    \end{split}
\end{align}
we can rewrite the Lipkin Hamiltonian from \cref{eq:theo:lipkin_second_quant_hamiltonian} using these
\begin{align}
    \begin{split} \label[eq]{eq:theo:lipkin_quasispin_hamiltonian}
        H_0 &= \epsilon J_z, \\
        H_1 &= \frac{1}{2}V (J_+^2 + J_-^2), \\
        H_2 &= \frac{1}{2}W ( \set{J_+ , J_- } - N ),
    \end{split}
\end{align}
These quasi spin operators obey the normal spin commutator relations
\begin{align*}
    &\commutator{J_z}{J_\pm} = \pm J_\pm, 
    &\commutator{J_+}{J_-} = 2 J_z, \\
    &\commutator{J^2}{J_\pm} = 0,
    &\commutator{J^2}{J_z} = 0,
\end{align*}
in addition to commuting with the number operator
\begin{align*}
    \commutator{N}{J_z} = \commutator{N}{J_\pm} = \commutator{N}{J^2} = 0.
\end{align*}
Using these relations we can show that the Hamiltonian (a product of quasi spin operators and the number operator) also commutes with  $J^2$, that is $\commutator{H}{J^2}=0$. Therefor $H$ and $J^2$ have shared eigenbasis, with $J$ being a `good` quantum number.

Using spin-eigenstates as the Hamiltonian basis, we define states through the normal approach $\ket{J,J_z}$ with $J$ and $ J_z$ as spin and spin-projections respectively. The states $J_z = \pm J$ are the easiest to construct, corresponding to a single level being completely filled. States in between can then be found using the quasi-spin ladder operators following

\begin{align}
    J_\pm \ket{J,J_z} &= \sqrt{J(J+1)-J_z (J_z \pm 1)} \ket{J,J_z \pm 1}. \label[eq]{eq:theo:ladder_operations}
\end{align}
Using this basis for the quasi-spin Hamiltonian from \cref{eq:theo:lipkin_quasispin_hamiltonian}, the explicit matrix $H_{J_z,J'_z} = \bra{J,J_z} H \ket{J,J_z'}$ can be constructed.

\comment{Rekkefølgen følger $\bra{J,-J} H \ket{J, -J}$ som $H_{0,0}$, motsatt av artikkelen}

\comment{Her med $W$, tror Morten har surra litt og her brukt hamiltonen $H = H_0 - H_1 - H_2$ samt uten $N$ operator}
\begin{align}
    H = \begin{pmatrix}
        -(\epsilon-W) & 0 & -V \\
        0 & -2W & 0 \\
        -V & 0 & \epsilon - W
    \end{pmatrix}
\end{align}

\comment{med $H = H_0 + H_1 + H_2$ og $N$ inkludert}
\begin{align}
    H = \begin{pmatrix}
        -\epsilon & 0 & V \\
        0 & W & 0 \\
        V & 0 & \epsilon
    \end{pmatrix}
\end{align}

\comment{$J=2$ er good med $H = H_0 + H_1 + H_2$}
\begin{align}
    H = \begin{pmatrix}
        -2\epsilon & 0  & \sqrt{6}V &0 &0 \\
        0 & -\epsilon + 3W & 0 & 3V & 0 \\
        \sqrt{6}V & 0 & 4W & 0 & \sqrt{6}V \\
        0 & 3V & 0 & \epsilon + 3W & 0 \\
        0 & 0 & \sqrt{6}V & 0 & 2\epsilon
    \end{pmatrix}
\end{align}

\subsection{Pauli Encoding Hamiltonians}
To apply a specific system to VQE, the Hamiltonian must be re-written in terms of a sum of \textit{Pauli strings}. Considering the identity $I$ and the three Pauli matrices $X, Y, Z$, we construct a specific term as a tensor product of these $P_i$. For an $n$-qubit system, we require $n-1$ tensor products. Combined with a weight $w_i$, the Hamiltonian must be written in the from
\begin{align}
    H = \sum_i w_i P_i \label[eq]{eq:theo:pauli_encoding_general}
\end{align}
For a general two-body Hamiltonian, this task can serve challenging. Many schemes exists for this purpose, such as the Jordan-Wigner transformation \citep{steudtnerMethodsSimulateFermions2019}. For the Lipkin model, an easier approach is available since the Hamiltonian can be written as products of the number and spin operators.

\subsection{Variational Principle}
The Rayleig-Ritz Variational Method claims that for a given Hamiltonian operator, \textbf{H}, the expectation value of a given state has a lower bound on the energy $E_0$, such that
\begin{equation}
    \frac{\bra{a}\boldsymbol{H}\ket{a}}{\braket{a}} \geq E_0
\end{equation}
This is a crucial method in perturbation theory, as it allows for the ability to approximate the lower bounds of the lowest eigenvalue of the Hamiltonian. It is the essential principle of the Variational Quantum Eigensolver. 

\section{Variational Quantum Eigensolver}
The Variational Quantum Eigensolver(VQE) takes on applying the Variational Principle, described above, minimizing the energy of 
\begin{equation}\label{VQE}
    E_{temp} = \frac{\bra{a}\boldsymbol{H}\ket{a}}{\braket{a}}
\end{equation}
with regards to altering the state $\ket{a}$. This is achieved by applying an ansatz to the initial state, in order to get an output eigenvalue, which further can be minimized. The ansatz takes \textit{n} Quantum Bits (qbits) and \textit{n} free parameters, $\theta_i$. The goal of the algorithm is to alter the parameters $\theta_i$ in order to achieve the optimal the minimal energy of the system, as computed in Eq. (\ref{VQE}). A schematic of the process is shown in Fig(\ref{}). The ansatz conjectured by Hlatshwayo et al. \cite{} is shown in Fig. (\ref{}). 
